Estimating Neighborhood Rents with Scraped Data

### 2018-06-05 manuscript/index.Rmd
almost...

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess"
date: "June 2, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    includes:
      in_header: "header.html"
      after_body: "../footer.html"
abstract: "Online classified ads are a key source of information about local rental housing markets. This research first assesses the agreement of census tract rent estimates based on scraped rental advertisements with existing data sources. The second component of the paper investivates temporal and spatial dynamics in one-bedroom rents among Seattle neighborhoods using spatial models. All models' posterior distribution are estimated with integrated nested Laplace approximations (INLA). Training data for models cover quarterly tract estimates for 2017 Q2 through 2018 Q1, while the test data are 2018 Q2 median values as observed through June 3rd. The top model assumes that spatial and temporal dynamics are separable, i.e. independent of each other, and non-interactive. This spatial random-effects model with AR(1) temporal structure achieves a mean absolute error (MAE) of about $100 for the training data and $140 for the test data."
---

@@

Demand for rental housing units in Seattle, WA surged in the past decade, due to relative scarcity in available housing amidst a period of historic population growth. Substantial appreciation for almost 2 years straight raised Seattle home prices to levels where [most households are no longer able to buy a home](https://www.seattletimes.com/business/real-estate/seattle-area-homebuyers-needed-11000-pay-raise-in-past-year-to-keep-up-with-rising-prices/?utm_source=The+Seattle+Times&utm_campaign=de86e2d581-Morning_Brief_11_28_2017&utm_medium=email&utm_term=0_5beb38b61e-de86e2d581-122931741) short of "driving till they qualify". More and more households must therefore rent to live in Seattle, and [almost half](http://www.jchs.harvard.edu/ARH_2017_cost_burdens_by_metro) of these renter households pay 30% of their incomes on housing costs, if not more. Given the universal need for housing, the individual dynamics related to rising housing costs have a role in shaping neighborhood processes of "demographic inversion" like urban gentrification and [suburbanizing poverty](https://www.brookings.edu/testimonies/the-changing-geography-of-us-poverty/) too.

Census data have common currency among scholars and practitioners interested in metropolitan housing markets, but neverthless possess a substantial limitation for research in tight housing markets like Seattle---that is, at least two years elapse between data collection and publication, if not more. This publication lag for these data prohibits analyzing market dynamics beyond long-term trends, particularly for smaller areas of aggregation like neighborhoods where the estimate may be an average of survey responses from a 5 year period. While more up-to-date options for neighborhood rent data exist through privately-held companies, such data can be somewhat of a black box in their creation and may be biased towards the costs of corporate-held properties. This would-be problem for academic researchers creates an opportunity for applying web scraping methods to generate a novel data on housing availability and costs.

This study demonstrates why scraped rental housing listings are a valuable source of data in subject areas such as housing studies and neighborhood demography. I draw on a set of descriptive analyses and models of quarterly rent levels among census tracts in Seattle, WA for this research objective. Summaries of the Craigslist data show agreement with existing sources in their distribution but do suggest higher median levels for most neighborhoods, likely given the listings' recent collection relative to other data. The models use a quarterly panel of observed neighborhood median one-bedroom rents and produce temporally and spatially smoothed predictions about neighborhood rent levels. The best model specification in terms of forecasting Q2 2018 based on Q1 2017 and Q1 2018 has a combination of local spatial smoothing and autoregression (order 1), with an average forecast error of about $140 or 8% for what. In a more general sense, the methods and frameworks used in this study also offer a template for efficiently collecting web data, conducting reproducible research, and publishing interactive results to GitHub.

@@

Existing public data are essentially limited to the [American Community Survey (ACS)](https://www.census.gov/programs-surveys/acs/) and [American Housing Survey (AHS)](https://www.census.gov/programs-surveys/ahs.html) following the cessation of long-form decennial censuses in 2000. These data theoretically have two sources of error relative to the ``true'' current median rent for a market and  neighborhood approximations like census tracts. Census sources of rental information cannot provide insight into any change in rental cost associated with newer developments becoming available (at least not until considerable time has already passed) given the temporal delay in data publication (i.e. ACS estimates are usually at least 2 years old, decennial many more). This feature of Census data is salient given newer housing units' generally higher rents and greater-than-average vacancy, both factors which lead to underestimating the present levels of rents for available housing units when either the ACS or decennial census are used as a current indicator. For already-leased rental housing units that are sampled, the temporal lag generates measurement error such that data on a given building's current asking rents may be underestimated relative to current tenants' payment levels.

@@

[Helena](http://helena-lang.org) is a high-level programming language for end users to automate web scraping as a method of data collection. Users write programs in an extension for Google Chrome by demonstrating the first row of data they want to collect using clicks, form interactions and highlighting values. The extension translates an initial demonstration into a starting script written in Helena, which a user can further modify or set to run on a regular schedule. Though Helena programs collect data roughly at the speed they are recorded at, users can run multiple programs in parallel to increase the volume of data collected. Data accumulate on a remote server (soon-to-be AWS) where users can later query either the full table of scraped data or a subset scraped within a specified number of hours.

@@

For the UW team's data collection, a Helena program runs 24-hours a day and scrapes listings from the Seattle Craigslist. It is important to note that web scraping does violate Craigslist's Terms of Service, and that we are using all scraped data exclusively for academic research. For a more thorough discussion of this issue, consult page 3 of [Boeing and Waddell (2016)](https://arxiv.org/ftp/arxiv/papers/1605/1605.05397.pdf).

@@

The following series of graphics summarize the listing data collected to date and compare rent estimates from these data to ACS data and Dupre+Scott. In an attempt to compare summaries about like rental units as much as possible, visualizations focus on one-bedroom units in all but one instance. One-bedroom units are tied with the combined share of two and three bedroom units for the [most common unit bedroom size](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/16_1YR/S2504/1600000US5363000) in Seattle according to 2016 ACS data. For Figure 2, data limitations require that the comparison is all housing units since ACS only recently (i.e. 2015-2016) started publishing bedroom-specific rent levels.

@@

The focus of the data description now turns towards estimating median rents for specific neighborhoods. While zip codes, unofficial City neighborhoods and even arbitrary grid geographies can all be used to aggregate micro-data about rental housing, we compare census tract estimates because they roughly approximate neighborhood-size units and can be linked with a variety of other data in Seattle and more generally. The following links provide reference maps for Seattle Census tracts ([2000](https://www.seattle.gov/Documents/Departments/OPCD/Demographics/GeographicFilesandMaps/2000CensusSeattleTractMap.pdf) and [2010](https://www.seattle.gov/Documents/Departments/OPCD/Demographics/GeographicFilesandMaps/2010CensusTractsandZipCodeBoundaries.pdf))

@@

An alternative explanation fpr the difference between measures comes in considering the units these properties are sampling from in a given neighborhood. The greater difference between the measures among lower-rent neighborhoods (with Craigslist estimating these as more expensive than Dupre+Scott) provides some evidence for this theory. These tracts are found towards the North and South edges of the city, and generally are more residential neighborhoods where 20+ unit apartment complexes are not the entire stock of rental unit properties. In these tracts, Craigslist has a non-zero probability of sampling from any larger building but also small houses, duplex/triplexes, mother-in-law suites and recently, [Accessory Dwelling Units (ADUs)](http://www.seattle.gov/DPD/Publications/CAM/cam116a.pdf).

@@

The following models learn from the Craigslist data accumulated up till the prior quarter (i.e. `r as.yearqtr(Sys.Date())-1`) to accomplish a few different goals. The most prominent goal is to use the panel data's temporal and spatial structure to understand variation in rent levels over time and across space. A secondary goal is to forecast the Seattle neighborhood rent surface for the current quarter. Finally, the following models allow for relatively straightforward imputation of missing values based on time period and the rent values of proximate tracts (though there are only two tracts where we have never observed a one-bedroom listing).

I assume that the log of the median one-bedroom rent for Seattle neighborhoods is normally distributed and estimate the posterior distribution of parameters $\theta_{it}$ using [integrated nested Laplace approximations (INLA)](https://folk.ntnu.no/hrue/r-inla.org/papers/inla-rss.pdf) with the default, weakly-informative priors for all random-effects.

@@

Model                    | Abbr.   | Formula
------------------------ | ------- | ----------------------------------------------
Fixed Intercept          | int     | $\theta_{it} = \beta_0 + Qtr$
Non-Spatial              | ns      | $\theta_{it} = \beta_0 + \epsilon_i + Qtr$
Non-Spatial AR(1)        | nsar1   | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i$
BYM Spatial AR(1)        | bym     | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i + S_i.$
BYM Spatiotemporal AR(1) | spt     | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i + S_i. + \epsilon_{it}$

The Fixed Intercept model (int) uses fixed effects for quarters only. The Non-Spatial (ns) model adds random noise (i.i.d.) tract random-effects. The Non-Spatial AR(1) model (nsar1) uses AR(1) process to model the temporal dynamics (formally, $\epsilon_1 \sim \mbox{Normal}(0, (\tau(1-\rho^2))^{-1}))$ where $\epsilon_t = \rho x_{t-1} + \epsilon_t$). This model includes a random noise term for each quarter too.

The BYM Spatial with AR(1) is the [Besags-York-Mollie (1991)](https://link.springer.com/article/10.1007/BF00116466) intrinsic conditional autoregressive spatial model with AR(1) and exchangeable hyperparameters for the panel's temporal structure. The random-effect $S_i$ is assumed to come from a normal distribution whose mean is the mean of the neighbors' random effects and variance proportional to the number of neighbors (formally, $S_i|S_j, j \in ne(i) ~ \mbox{Normal}(\bar{S_i}, \frac{\sigma^{2}_s}{m_j})$. Lastly, the BYM Spatiotemporal AR(1) (spt) adds an exchangeable random-effect for each period to allow for area-specific deviations in time trends.

@@

Visit the interactive results dashboard [here](http://hesscl.com/smooth-sea/dashboard/index.html).

@@

@@

@@

ggplot(bym_df %>% filter(model == "E. Spatial AR(1)"), 
         aes(x = listingQtr, y = value, group = GISJOIN, color = qtrDev, label = GISJOIN)) +
  geom_line(lwd = .25, color = "black", alpha = .5) +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  scale_color_viridis_c(option = "A", labels = scales::dollar) +
  xlab("") +
  ylab("Median 1B Rent\n") +
  labs(color="Quarterly\nDeviation") +
  theme_minimal() +
  ggsave(filename = "../output/bym_lineplot.png",
         width = 6, height = 4, dpi = 500)
```

![**Figure 6.** _Lineplot of Spatial AR(1) model predicted values._](../output/bym_lineplot.png)

@@

@@

@@

>>>>

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess and Sarah Chasins"
date: "June 2, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    includes:
      in_header: "header.html"
      after_body: "../footer.html"
abstract: "Online classified ads are a key source of information about local rental housing markets. This research first assesses the agreement of census tract rent estimates based on scraped rental advertisements with existing data sources. The second component of the paper investivates temporal and spatial dynamics in one-bedroom rents among Seattle neighborhoods using spatial models. All models' posterior distribution are estimated with integrated nested Laplace approximations (INLA). Training data for models cover quarterly tract estimates for 2017 Q2 through 2018 Q1, while the test data are 2018 Q2 median values as observed through June 3rd. The top model assumes that spatial and temporal dynamics are separable, i.e. independent of each other, and non-interactive. This spatial random-effects model with AR(1) temporal structure achieves a mean absolute error (MAE) of about $100 for the training data and $140 for the test data."
---

@@

Demand for rental housing units in Seattle, WA surged in the past decade, due to relative scarcity in available housing amidst a period of [historic population growth](https://www.seattletimes.com/seattle-news/data/114000-more-people-seattle-now-this-decades-fastest-growing-big-city-in-all-of-united-states/){target="_blank"}. Substantial appreciation for almost 2 years straight raised Seattle home prices to levels where [most households are no longer able to buy a home](https://www.seattletimes.com/business/real-estate/seattle-area-homebuyers-needed-11000-pay-raise-in-past-year-to-keep-up-with-rising-prices/?utm_source=The+Seattle+Times&utm_campaign=de86e2d581-Morning_Brief_11_28_2017&utm_medium=email&utm_term=0_5beb38b61e-de86e2d581-122931741){target="_blank"} short of "driving till they qualify". More and more households must therefore rent to live in Seattle, and [almost half](http://www.jchs.harvard.edu/ARH_2017_cost_burdens_by_metro){target="_blank"} of these renter households pay 30% of their incomes on housing costs, if not more. Given the universal need for housing, the individual dynamics related to rising housing costs have a role in shaping neighborhood processes of "demographic inversion" like urban gentrification and [suburbanizing poverty](https://www.brookings.edu/testimonies/the-changing-geography-of-us-poverty/){target="_blank"} too.

Census data have common currency among scholars and practitioners interested in metropolitan housing markets, but neverthless possess a substantial limitation for research in tight housing markets like Seattle---that is, at least two years elapse between data collection and publication, if not more. This publication lag prohibits analyzing market dynamics beyond long-term trends, particularly for smaller areas of aggregation like neighborhoods where the estimate may be an average of survey responses from a 5 year period. While more up-to-date options for neighborhood rent data exist through privately-held companies, such data can be somewhat of a black box in their creation and may be biased towards the costs of corporate-held properties. This would-be problem for academic researchers creates an opportunity for applying web scraping methods to generate a novel data on housing availability and costs.

This study demonstrates why scraped rental housing listings are a valuable source of data in subject areas such as housing studies and neighborhood demography. I draw on a set of descriptive analyses and models of quarterly rent levels among census tracts in Seattle, WA for this research objective. Summaries of the Craigslist data show agreement with existing sources in their distribution but do suggest higher median levels for most neighborhoods, likely given the listings' recent collection relative to other data. The models use a quarterly panel of observed neighborhood median one-bedroom rents and produce temporally- and spatially-smoothed predictions about neighborhood rent levels. The best model specification in terms of forecasting Q2 2018 based on Q1 2017 through Q1 2018 has a combination of local spatial smoothing and autoregression (order 1), with an average forecast error of about $140 or 8% relative to the median neighborhood. In a more general sense, the methods and frameworks used in this study also offer a template for efficiently collecting web data, conducting reproducible research, and publishing interactive results to GitHub.

@@

Existing public data are essentially limited to the [American Community Survey (ACS)](https://www.census.gov/programs-surveys/acs/) and [American Housing Survey (AHS)](https://www.census.gov/programs-surveys/ahs.html){target="_blank"} following the cessation of long-form decennial censuses in 2000. These data theoretically have two sources of error relative to the "true"" current median rent for a market and neighborhood approximations like census tracts. Census sources of rental information cannot provide insight into any change in rental cost associated with newer developments becoming available (at least not until considerable time has already passed) given the temporal delay in data publication. This feature of Census data is salient given newer housing units' generally higher rents and greater-than-average vacancy, both factors which lead to underestimating the present levels of rents for available housing units when either the ACS or decennial census are used as a current indicator. For already-leased rental housing units that are sampled, the temporal lag generates measurement error such that data on a given building's current asking rents may be underestimated relative to current tenants' payment levels.

@@

[Helena](http://helena-lang.org){target="_blank"} is a high-level programming language aimed at helping end users automate web scraping as a method of data collection. Users write programs in an extension for Google Chrome by demonstrating the first row of data they want to collect using clicks, form interactions and highlighting values. The extension translates an initial demonstration into a starting script written in Helena, which a user can further modify or set to run on a regular schedule. Though Helena programs collect data roughly at the speed they are recorded at, users can run multiple programs in parallel to increase the volume of data collected. Data accumulate on a remote server (soon-to-be AWS) where users can later query either the full table of scraped data or a subset scraped within a specified number of hours.

@@

For the UW team's data collection, a Helena program runs 24-hours a day and scrapes listings from the Seattle Craigslist. It is important to note that web scraping does violate Craigslist's Terms of Service, and that we are using all scraped data exclusively for academic research. For a more thorough discussion of this issue, consult page 3 of [Boeing and Waddell (2016)](https://arxiv.org/ftp/arxiv/papers/1605/1605.05397.pdf){target="_blank"}.

@@

The following series of graphics summarize the listing data collected to date and compare rent estimates from these data to ACS data and Dupre+Scott. In an attempt to compare summaries about like rental units as much as possible, visualizations focus on one-bedroom units in all but one instance. One-bedroom units are tied with the combined share of two and three bedroom units for the [most common unit bedroom size](https://factfinder.census.gov/bkmk/table/1.0/en/ACS/16_1YR/S2504/1600000US5363000){target="_blank"} in Seattle according to 2016 ACS data. For Figure 2, data limitations require that the comparison is all housing units since ACS only recently (i.e. 2015-2016) started publishing bedroom-specific rent levels.

@@

The focus of the data description now turns towards estimating median rents for specific neighborhoods. While zip codes, unofficial City neighborhoods and even arbitrary grid geographies can all be used to aggregate micro-data about rental housing, we compare census tract estimates because they roughly approximate neighborhood-size units and can be linked with a variety of other data in Seattle and more generally. The following links provide reference maps for Seattle Census tracts ([2000](https://www.seattle.gov/Documents/Departments/OPCD/Demographics/GeographicFilesandMaps/2000CensusSeattleTractMap.pdf){target="_blank"} and [2010](https://www.seattle.gov/Documents/Departments/OPCD/Demographics/GeographicFilesandMaps/2010CensusTractsandZipCodeBoundaries.pdf){target="_blank"})

@@

An alternative explanation fpr the difference between measures comes in considering the units these properties are sampling from in a given neighborhood. The greater difference between the measures among lower-rent neighborhoods (with Craigslist estimating these as more expensive than Dupre+Scott) provides some evidence for this theory. These tracts are found towards the North and South edges of the city, and generally are more residential neighborhoods where 20+ unit apartment complexes are not the entire stock of rental unit properties. In these tracts, Craigslist has a non-zero probability of sampling from any larger building but also small houses, duplex/triplexes, mother-in-law suites and recently, [Accessory Dwelling Units (ADUs)](http://www.seattle.gov/DPD/Publications/CAM/cam116a.pdf){target="_blank"}.

@@

The following models learn from Craigslist data accumulated up till the prior quarter (i.e. `r as.yearqtr(Sys.Date())-1`) to accomplish a few different goals. The most prominent goal is to use the panel data's temporal and spatial structure to understand variation in rent levels over time and across space. A secondary goal is to forecast the Seattle neighborhood rent surface for the current quarter. Finally, the following models allow for relatively straightforward imputation of missing values based on time period and the rent values of proximate tracts.

I assume that the log of the median one-bedroom rent for Seattle neighborhoods is normally distributed and estimate the posterior distribution of parameters $\theta_{it}$ using [integrated nested Laplace approximations (INLA)](https://folk.ntnu.no/hrue/r-inla.org/papers/inla-rss.pdf){target="_blank"} with the default, weakly-informative priors for all random-effects. I choose to log the dependent variable because all values are positive and this transformation improves model fit.

@@

Model                    | Abbr.   | Formula
------------------------ | ------- | ----------------------------------------------
Fixed Intercept          | `int`     | $\theta_{it} = \beta_0 + Qtr$
Non-Spatial              | `ns`      | $\theta_{it} = \beta_0 + \epsilon_i + Qtr$
Non-Spatial AR(1)        | `nsar1`  | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i$
BYM Spatial AR(1)        | `bym `    | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i + S_i.$
BYM Spatiotemporal AR(1) | `spt`     | $\theta_{it} = \beta_0 + \epsilon_t + \epsilon_{t-1} + \epsilon_i + S_i. + \epsilon_{it}$

The Fixed Intercept model (`int`) uses fixed effects for quarters only. The Non-Spatial (`ns`) model adds random noise (i.i.d.) tract random-effects. The Non-Spatial AR(1) model (`nsar1`) uses AR(1) process to model the temporal dynamics (formally, $\epsilon_1 \sim \mbox{Normal}(0, (\tau(1-\rho^2))^{-1}))$ where $\epsilon_t = \rho x_{t-1} + \epsilon_t$). This model includes a random noise term for each quarter too.

The BYM Spatial with AR(1) is the [Besags-York-Mollie (1991)](https://link.springer.com/article/10.1007/BF00116466){target="_blank"} intrinsic conditional autoregressive spatial model with AR(1) and exchangeable hyperparameters for the panel's temporal structure (referred to as `bym` using shorthand). The random-effect $S_i$ is assumed to come from a normal distribution whose mean is the mean of the neighbors' random effects and variance proportional to the number of neighbors (formally, $S_i|S_j, j \in ne(i) ~ \mbox{Normal}(\bar{S_i}, \frac{\sigma^{2}_s}{m_j})$. Lastly, the BYM Spatiotemporal AR(1) (`spt`) adds an exchangeable random-effect for each period to allow for area-specific deviations in time trends.

@@

Visit the interactive results dashboard [here](http://hesscl.com/smooth-sea/dashboard/index.html){target="_blank"}.

@@

The following tables show in-sample and out-of-sample (i.e. 2018 Q2) accuracy for the 5 model specifications in terms of root mean squared-error (RMSE) and mean absolute error (MAE). Note how though the Non-Spatial models (i.e. `ns` and `nsar1`) achieve slightly better in-sample fits, both Spatial models are more accurate at predicting the current month's surface of rent values. It is important to note how the goal in the present case is to understand the data generating process, that is, the systematic variation in the data less the random component. So while we want to minimize model error as a way to judge if our models improve on each other, we also want to smooth over sampling variability in the Craigslist data that induces local deviations compared to the true median rent. The [information criteria for the models](http://hesscl.com/smooth-sea/dashboard/index.html#model-fit){target="_blank"} generally show that the spatial specifications are more likely models of the neighborhood rent data generating process.

@@

Figure 6 depicts the predicted temporal structure based on the top fitting model, the Spatial AR(1) specification. The quarterly fluctuation is about $50-$100 depending on the tract in question. Modeling neighborhood median rents on log scale allows for non-constant variance across the range of y, such that the periodic deviations are largest at the top of the distribution and more subdued among low-rent neighborhoods.

@@

ggplot(bym_df %>% filter(model == "E. Spatial AR(1)"), 
         aes(x = listingQtr, y = value, group = GISJOIN, color = qtrDev, label = GISJOIN)) +
  geom_line(lwd = .25, color = "black", alpha = .5) +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  scale_color_viridis_c(option = "A", labels = scales::dollar) +
  xlab("") +
  ylab("Median 1B Rent\n") +
  labs(color="Quarterly\nDeviation") +
  theme_minimal() +
  theme(legend.key.width = unit(.1, "inch")) +
  ggsave(filename = "../output/bym_lineplot.png",
         width = 6, height = 3, dpi = 500)
```

![**Figure 6.** _Lineplot of Spatial AR(1) model predicted values. Colors denote a tract's deviation from the average neighborhood 1B rent level on a quarter-by-quarter basis._](../output/bym_lineplot.png)

@@

Figure 7 provides a spatial time-series for the actual and predicted values using the Spatial AR(1) `bym` model. Since there is no space time interaction, the spatial distribution is constant across the quarter periods. The quarterly fluctuation is visible in both the observed and predicted data, though the spatial distribution of rent levels in the model predictions smooths over particularly high and low local deviations. The model imputes reasonable values for missing data over the entire panel, giving an estimate of what we would expect a one-bedroom to cost based on the period, neighbors and any earlier observations of the tract (if they exist). Overall, one clear takeaway is that the spatial variation in rent cost swamps that of the short-term dynamics observed to date. In this sense, estimating the spatial distribution completely and accurately is a crucial goal of any indicator of the market---whether a simple median or a complex model like the current one.

@@

This study highlights the importance of considering scraped web data for understanding the dynamics of neighborhood rental housing costs. Throughout this work we demonstrate how Craigslist rental housing listings scraped may be used to research the estimated rent for the Seattle market and its neighborhoods. Models

@@

[Boeing, G. and Waddell, P., 2017. New insights into rental housing markets across the united states: web scraping and analyzing craigslist rental listings. Journal of Planning Education and Research, 37(4), pp.457-476.](http://journals.sagepub.com/doi/abs/10.1177/0739456X16664789){target="_blank"}

[Besag, J., York, J. and Mollie, A., 1991. Bayesian image restoration with two applications in spatial statistics (with discussion) Annals of the Institute of Statistical Mathematics. 43, pp.1-59.](https://link.springer.com/article/10.1007/BF00116466){target="_blank"}

[Blangiardo, M., Cameletti, M., Baio, G. and Rue, H., 2013. Spatial and spatio-temporal models with R-INLA. Spatial and spatio-temporal epidemiology, 4, pp.33-49.](https://www.sciencedirect.com/science/article/pii/S1877584512000846){target="_blank"}
